Project 2

### 2021-10-09 project_2.Rmd
Commit
Sentiment Analysis

```{r load_libraries}
#loading all the necessary libraries
library(gutenbergr)
library(tidytext)
library(tidyverse)
library(readtext)
```

@@

```{r gutenberg_fitzgerald_download}
#downloading all the texts found
fitzgerald_download <- fitzgerald_text %>% 
                      gutenberg_download(meta_fields = c("title", "author"))
```
```{r import_Fitzgerald_books}
The_Great_Gatsby <- read_delim("The Great Gatsby_Fitzgerald, F. Scott (Francis Scott).txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
The_Great_Gatsby <- The_Great_Gatsby %>% mutate(author = "Fitzgerald, F. Scott (Francis Scott)", .after = text) %>% mutate(title = "The Great Gatsby", .before = author)

Tender_is_the_Night <- read_delim("Tender is the Night_Fitzgerald, F. Scott (Francis Scott).txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
Tender_is_the_Night <- Tender_is_the_Night %>% mutate(author = "Fitzgerald, F. Scott (Francis Scott)", .after = text) %>% mutate(title = "Tender is the Night", .before = author)
```

@@

The_Sun_Also_Rises_Hemingway_Ernest <- read_delim("The Sun Also Rises_Hemingway, Ernest.txt", 
    delim = "\t", quote = "\\\"", escape_double = FALSE, 
    trim_ws = TRUE)
The_Sun_Also_Rises_Hemingway_Ernest <- The_Sun_Also_Rises_Hemingway_Ernest %>% mutate(author = "Hemingway, Earnest", .after = text) %>% mutate(title = "The Sun Also Rises", .before = author)

The_Old_Man_and_the_Sea_Hemingway_Ernest <- read_delim("The Old Man and the Sea_Hemingway, Ernest.txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
The_Old_Man_and_the_Sea_Hemingway_Ernest <- The_Old_Man_and_the_Sea_Hemingway_Ernest %>% mutate(author = "Hemingway, Earnest", .after = text) %>% mutate(title = "The Old Man and the Sea", .before = author)

For_Whom_the_Bell_Tolls_Hemingway_Ernest <- read_delim("For Whom the Bell Tolls_Hemingway, Ernest.txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
For_Whom_the_Bell_Tolls_Hemingway_Ernest <- For_Whom_the_Bell_Tolls_Hemingway_Ernest %>% mutate(author = "Hemingway, Earnest", .after = text) %>% mutate(title = "For Whom The Bell Tolls", .before = author)

A_Farewell_to_Arms_Hemingway_Ernest <- read_delim("A Farewell to Arms_Hemingway, Ernest.txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
A_Farewell_to_Arms_Hemingway_Ernest <- A_Farewell_to_Arms_Hemingway_Ernest %>% mutate(author = "Hemingway, Earnest", .after = text) %>% mutate(title = "A Farewell to Arms", .before = author)

@@

@@

```{r exporting_tables}
save(author_table, file = "saved_data.rda")
```

>>>>

```{r load_libraries}
#loading all the necessary libraries
library(gutenbergr)
library(tidytext)
library(tidyverse)
library(readtext)
library(sentimentr)
```

@@

```{r gutenberg_fitzgerald_download}
#downloading all the texts found
fitzgerald_download <- fitzgerald_text %>% 
                      gutenberg_download(meta_fields = c("title", "author"))
```
```{r import_Fitzgerald_books}
The_Great_Gatsby <- read_delim("The Great Gatsby_Fitzgerald, F. Scott (Francis Scott)_clean.txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
The_Great_Gatsby <- The_Great_Gatsby %>% mutate(author = "Fitzgerald, F. Scott (Francis Scott)", .after = text) %>% mutate(title = "The Great Gatsby", .before = author)

Tender_is_the_Night <- read_delim("Tender is the Night_Fitzgerald, F. Scott (Francis Scott)_clean.txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
Tender_is_the_Night <- Tender_is_the_Night %>% mutate(author = "Fitzgerald, F. Scott (Francis Scott)", .after = text) %>% mutate(title = "Tender is the Night", .before = author)
```

@@

The_Sun_Also_Rises_Hemingway_Ernest <- read_delim("The Sun Also Rises_Hemingway, Ernest_clean.txt", 
    delim = "\t", quote = "\\\"", escape_double = FALSE, 
    trim_ws = TRUE)
The_Sun_Also_Rises_Hemingway_Ernest <- The_Sun_Also_Rises_Hemingway_Ernest %>% mutate(author = "Hemingway, Earnest", .after = text) %>% mutate(title = "The Sun Also Rises", .before = author)

The_Old_Man_and_the_Sea_Hemingway_Ernest <- read_delim("The Old Man and the Sea_Hemingway, Ernest_clean.txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
The_Old_Man_and_the_Sea_Hemingway_Ernest <- The_Old_Man_and_the_Sea_Hemingway_Ernest %>% mutate(author = "Hemingway, Earnest", .after = text) %>% mutate(title = "The Old Man and the Sea", .before = author)

For_Whom_the_Bell_Tolls_Hemingway_Ernest <- read_delim("For Whom the Bell Tolls_Hemingway, Ernest_clean.txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
For_Whom_the_Bell_Tolls_Hemingway_Ernest <- For_Whom_the_Bell_Tolls_Hemingway_Ernest %>% mutate(author = "Hemingway, Earnest", .after = text) %>% mutate(title = "For Whom The Bell Tolls", .before = author)

A_Farewell_to_Arms_Hemingway_Ernest <- read_delim("A Farewell to Arms_Hemingway, Ernest_clean.txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
A_Farewell_to_Arms_Hemingway_Ernest <- A_Farewell_to_Arms_Hemingway_Ernest %>% mutate(author = "Hemingway, Earnest", .after = text) %>% mutate(title = "A Farewell to Arms", .before = author)

@@

```{r new_sentiment_analysis}
#temp <- hemingway_corpus %>% unnest_regex(sentences, text, pattern = "[.?!]", to_lower = TRUE)
my_text <- read_file("The Great Gatsby_Fitzgerald, F. Scott (Francis Scott)_clean.txt")
my_text <- get_sentences(my_text)
total_sentiment <- sentiment(my_text)
total <- sum(total_sentiment$sentiment)
```

```{r all_authors}
all_authors <- bind_rows(fitzgerald_corpus, hemingway_corpus)

```{r tidy_all_authors}
tidy_all_authors <- all_authors %>% unnest_tokens(word, text) %>% anti_join(stop_words)
```

@@

## Sentiment Analysis

```{r all_author_sentences}
all_authors_sentence <- all_authors %>%
  group_by(author, title, text) %>%
  summarise (text = paste(text, collapse = "")) %>%
  unnest_regex(sentences, text, pattern = "[.?!]", to_lower = TRUE)  
```

```{r author_sentence_nr}
author_sentence_nr <- all_authors_sentence %>%
  ungroup() %>%
  mutate(sentence_number = row_number()) %>%
  group_by(author, title, sentence_number) %>%
  unnest_tokens(word, sentences) %>%
  anti_join(stop_words)
```

```{r author_concept}
author_concept <-  author_sentence_nr #%>%
  #left_join(emotion_words) 
```

```{r author_concept_sentiment}
author_concept_sentiment <- author_concept %>%
  inner_join(get_sentiments("bing"))
```

```{r author_sentiment_total}
author_sentiment_total <- author_concept_sentiment %>%
  count(sentence_number, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0)  %>%
  mutate(sentiment = positive - negative) #%>%
  #left_join(author_concept) #%>%
  #filter(emotion == TRUE)
```

```{r author_sentiment_table}
author_sentiment_table <- author_sentiment_total %>%
  #pivot_longer(sentiment,
               #names_to = "word",
               #values_to = "total_sentiment")  %>%
  #drop_na() %>%
  group_by(title, author) %>%
  summarise (total = sum(sentiment)) %>%
  ungroup()
```

```{r author_sentiment_plot}
author_sentiment_table %>%
  ggplot(aes(title, y = total, fill = title)) +
  geom_col(color = "black",
           alpha = .7,
           position = "identity") +
  #facet_wrap(~ concept) +
  labs(title = "Positive and Negative Sentiment by Concept",
       x = "Overal Sentiment",
       y = "Author",
       fill = "Title") +
  coord_flip() 
```

```{r exporting_tables}
save(author_table, hemingway_corpus, file = "saved_data.rda")
```
